Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-22 main.tex
small edit in the beginning of Model section (addresses 2 reviewer´s complaints)

    We first describe the model for our target applications, which are (large scientific) workflows for which we do not have perfect a priori knowledge,
    in Section~\ref{sec.mod.work}.  Next, we define the execution
    environment, a heterogeneous system (in terms of processor speed and memory size),
    in Section~\ref{sec.mod.plat}. Finally, we present the optimization problem in
    Section~\ref{sec.mod.pb}. The key notation is summarized in Table~\ref{tabnotation}.

>>>>

    We first describe the model for our target applications, large scientific workflows for which we do not have exact a priori knowledge,
    in Section~\ref{sec.mod.work}.  Next, we define the execution
    environment, a cluster that is heterogeneous in terms of processor speed and memory size,
   in Section~\ref{sec.mod.plat}. Finally, we present the optimization problem in
    Section~\ref{sec.mod.pb}. The key notation is summarized in Table~\ref{tabnotation}.
